Optimizing and Incrementalizing Collection Queries by AST Transformations

### 2017-08-07 Abstract.tex
Fix typos in Abstract.tex

To incrementalize higher-order programs by program transformation, we extend
\emph{finite differencing} \citep{Paige82FDC,Blakeley:1986:EUM,Gupta99MMV} and
develop the first approach to incrementalization by program transformation for
higher-order programs. Base programs are transformed to \emph{derivatives},
program that transform input \emph{changes} to output changes.
We prove that our incrementalization approach is correct: We develop the theory
underlying this approach for simply-typed and untyped $\lambda$-calculus, and
discuss extensions to System F\@.

@@

For efficient incrementalization, it is necessary to choose and incrementalize
by hand appropriate primitive operations. We incrementalize a significant subset
of collection operations and perform case studies, showing order-of-magnitude
both in practice and in asymptotic complexity.
% To incrementalize programs efficiently, derivatives
% To use our approach a certain domain, designers must provide
% relies on efficient primitives

>>>>

To incrementalize higher-order programs by program transformation, we extend
\emph{finite differencing} \citep{Paige82FDC,Blakeley:1986:EUM,Gupta99MMV} and
develop the first approach to incrementalization by program transformation for
higher-order programs. Base programs are transformed to \emph{derivatives},
programs that transform input \emph{changes} to output changes.
We prove that our incrementalization approach is correct: We develop the theory
underlying this approach for simply-typed and untyped $\lambda$-calculus, and
discuss extensions to System F\@.

@@

For efficient incrementalization, it is necessary to choose and incrementalize
by hand appropriate primitive operations. We incrementalize a significant subset
of collection operations and perform case studies, showing order-of-magnitude speedups
both in practice and in asymptotic complexity.
% To incrementalize programs efficiently, derivatives
% To use our approach a certain domain, designers must provide
% relies on efficient primitives
